---
title: "FORCE Level 2 Processing Report"
date: "`r Sys.Date()`"
output: html_document
params:
  dlog: "log"
  ftable: NULL
---
  
```{r load-packages, include = FALSE}
require(dplyr)
require(tidyr)
require(echarts4r)
```

```{r define_barplot, echo = FALSE, warning = FALSE}
e_bars_stacked <- function(df, x){
  cols <- setdiff(names(df), x)
  
  fig <- df |>
    e_charts_(x)
  
  for (col in cols) {
    fig <- do.call(e_bar, list(fig, as.name(col), name = col, stack = "stack"))
  }
  fig
}

theme <- "westeros"

e_common(theme = theme)

get_theme_colors <- function(theme = "auritus"){
  path <- system.file("htmlwidgets/lib/echarts-6.0.0/themes", package = "echarts4r")
  file <- paste0(path, "/", theme, ".js")
  js_lines <- readLines(file)
  palette <- unlist(regmatches(js_lines, gregexpr("#[0-9a-fA-F]{6}", js_lines)))
}
colors <- get_theme_colors(theme)
```

```{r load-data, include = FALSE}
flog <- params$dlog %>% dir(".log$", full.names = TRUE)
nlog <- flog %>% length()

log <- "character" %>% vector(nlog)
id <- "character" %>% vector(nlog)

for (i in 1:nlog) {
  
  tmp <- readLines(flog[i])
  
  if (length(grep("Image:", tmp)) > 0){
    id[i] <- tmp %>% 
      grep("Image:", ., value = TRUE) %>%
      gsub("/ ", "", .) %>%
      basename()
  } else {
    id[i] <- tmp %>% 
      paste(collapse = " ") %>%
      gsub(":.*", "", .) %>%
      gsub("/ ", "", .) %>%
      basename()
  }
  
  log[i] <- tmp %>%
    paste(collapse = " ") %>%
    gsub(".*Start core processing", "", .) %>%
    gsub("Core processing signaled.*", "", .)
  
}
```

```{r prepare-data, include = FALSE}
status <- rep("Error", nlog)
status[grep("Success", log)]      <- "Success"
status[grep("Skip", log)]         <- "Too cloudy"
status[grep("coreg failed", log)] <- "Coregistration failed"
status <- status %>% as.factor()
nfail <- sum(status == "Error")

mm <- log %>%
  gsub(".*([0-9]{2}) mins.*", "\\1", .) %>%
  as.numeric()
ss <- log %>%
  gsub(".*([0-9]{2}) secs.*", "\\1", .) %>%
  as.numeric()
time <- mm + ss / 60

id_split <- id %>% strsplit("_")

sensor <- id_split %>% sapply("[", 1)

date <- id_split %>%
  sapply(function(x) {
    grep("^[0-9]{8}", x, value = TRUE) %>%
      first() }) %>%
  substr(1, 8) %>%
  strptime("%Y%m%d")

dc <- log %>%
  gsub(".*dc: ([^%]*)%.*", "\\1", .) %>%
  as.numeric()

cc <- log %>%
  gsub(".*cc: ([^%]*)%.*", "\\1", .) %>%
  as.numeric()

sc <- log %>%
  gsub(".*sc: ([^%]*)%.*", "\\1", .) %>%
  as.numeric()

wc <- log %>%
  gsub(".*wc: ([^%]*)%.*", "\\1", .) %>%
  as.numeric()

ac <- 100 %>%
  `-`(cc + sc) %>%
  pmax(0)
lc <- 100 %>%
  `-`(cc + sc + wc) %>%
  pmax(0)

aod <- log %>%
  gsub(".*AOD: (.*)\\. #.*", "\\1", .) %>%
  as.numeric()

nwater <- log %>%
  gsub(".*# of targets: ([0-9]*)/.*", "\\1", .) %>%
  as.integer()

nveg <- log %>%
  gsub(".*# of targets: [0-9]*/([0-9]*).*", "\\1", .) %>%
  as.integer()

aod_status <- rep("NA", nlog)
aod_status[(nwater + nveg) == 0] <- "AOD estimation failed"
aod_status[(nwater + nveg)  > 0] <- "AOD estimation successful"
aod_status <- aod_status %>% as.factor()

nchip <- log %>%
  gsub(".* ([0-9]*) product.*", "\\1", .) %>%
  as.integer()

data <- data.frame(status,
                   sensor,
                   nchip,
                   time,
                   date,
                   year  = format(date, "%Y"),
                   month = format(date, "%m"),
                   week  = format(date, "%W"),
                   doy       = format(date, "%j"),
                   yearhalf  = paste(
                     format(date, "%Y"),
                     format(date, "%m") %>%
                       as.integer() %>%
                       `/`(6) %>%
                       ceiling(),
                     sep = "-"
                   ),
                   yearquarter  = paste(
                     format(date, "%Y"),
                     format(date, "%m") %>%
                       as.integer() %>%
                       `/`(3) %>%
                       ceiling(),
                     sep = "-"
                   ),
                   yearmonth = format(date, "%Y-%m"),
                   dc,
                   cc,
                   sc,
                   wc,
                   ac,
                   lc,
                   aod_status,
                   aod,
                   nwater,
                   nveg,
                   log,
                   id)
```

## Processing status

`r nlog` Level 1 images were processed.
`r nfail` images failed.

```{r plot-status, echo = FALSE, warning = FALSE}
data |>
  count(status, name = "Number") |>
  e_charts(status) |>
  e_pie(Number, radius = c("30%", "70%"), roseType = "radius") |>
  e_tooltip(trigger = "item")
```

```{r failed-images, echo = FALSE}
if (nfail > 0) {
  data %>% filter(status == "Error") %>% select(log)
}
```

## Number of Level 1 images

The following plots count the number of processed Level 1 images per sensor, year, month and week.
*Processing status is not taken into account.*

```{r plot-l1-sensor, echo = FALSE, warning = FALSE}
data %>% 
  count(sensor, name = "Number") %>%
  arrange(sensor) |>
  e_charts(sensor) |>
  e_pie(Number, radius = c("30%", "70%"), roseType = "radius") |>
  e_tooltip(trigger = "item") |>
  e_group("sensor")
```

```{r plot-l1-year, echo = FALSE, warning = FALSE}
data %>% 
  mutate(year = as.factor(year)) |>
  count(sensor, year, name = "Number") %>%
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(year) |>
  e_bars_stacked("year") |>
  e_y_axis(name = "# of L1 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l1-yearhalf, echo = FALSE, warning = FALSE}
data %>% 
  mutate(yearhalf = as.factor(yearhalf)) |>
  count(sensor, yearhalf, name = "Number") %>%
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(yearhalf) |>
  e_bars_stacked("yearhalf") |>
  e_y_axis(name = "# of L1 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l1-yearquarter, echo = FALSE, warning = FALSE}
data %>% 
  mutate(yearquarter = as.factor(yearquarter)) |>
  count(sensor, yearquarter, name = "Number") %>%
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(yearquarter) |>
  e_bars_stacked("yearquarter") |>
  e_y_axis(name = "# of L1 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l1-yearmonth, echo = FALSE, warning = FALSE}
data %>% 
  mutate(yearmonth = as.factor(yearmonth)) |>
  count(sensor, yearmonth, name = "Number") %>%
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(yearmonth) |>
  e_bars_stacked("yearmonth") |>
  e_y_axis(name = "# of L1 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l1-month, echo = FALSE, warning = FALSE}
data %>% 
  mutate(month = as.factor(month)) |>
  count(sensor, month, name = "Number") %>%
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(month) |>
  e_bars_stacked("month") |>
  e_y_axis(name = "# of L1 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l1-week, echo = FALSE, warning = FALSE}
data %>% 
  mutate(week = as.factor(week)) |>
  count(sensor, week, name = "Number") %>%
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(week) |>
  e_bars_stacked("week") |>
  e_y_axis(name = "# of L1 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

## Number of Level 2 images

The following plots count the number of processed Level 2 image chips per sensor, year, month and week.

```{r plot-l2-sensor, echo = FALSE, warning = FALSE}
data %>% 
  group_by(sensor) %>%
  summarise(Number = sum(nchip, na.rm = TRUE), .groups = "drop") |>
  arrange(sensor) |>
  e_charts(sensor) |>
  e_pie(Number, radius = c("30%", "70%"), roseType = "radius") |>
  e_tooltip(trigger = "item") |>
  e_group("sensor")
```

```{r plot-l2-year, echo = FALSE, warning = FALSE}
data %>% 
  mutate(year = as.factor(year)) |>
  group_by(sensor, year) %>%
  summarise(Number = sum(nchip, na.rm = TRUE), .groups = "drop") |>
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(year) |>
  e_bars_stacked("year") |>
  e_y_axis(name = "# of L2 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l2-yearhalf, echo = FALSE, warning = FALSE}
data %>% 
  mutate(yearhalf = as.factor(yearhalf)) |>
  group_by(sensor, yearhalf) %>%
  summarise(Number = sum(nchip, na.rm = TRUE), .groups = "drop") |>
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(yearhalf) |>
  e_bars_stacked("yearhalf") |>
  e_y_axis(name = "# of L2 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l2-yearquarter, echo = FALSE, warning = FALSE}
data %>% 
  mutate(yearquarter = as.factor(yearquarter)) |>
  group_by(sensor, yearquarter) %>%
  summarise(Number = sum(nchip, na.rm = TRUE), .groups = "drop") |>
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(yearquarter) |>
  e_bars_stacked("yearquarter") |>
  e_y_axis(name = "# of L2 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l2-yearmonth, echo = FALSE, warning = FALSE}
data %>% 
  mutate(yearmonth = as.factor(yearmonth)) |>
  group_by(sensor, yearmonth) %>%
  summarise(Number = sum(nchip, na.rm = TRUE), .groups = "drop") |>
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(yearmonth) |>
  e_bars_stacked("yearmonth") |>
  e_y_axis(name = "# of L2 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l2-month, echo = FALSE, warning = FALSE}
data %>% 
  mutate(month = as.factor(month)) |>
  group_by(sensor, month) %>%
  summarise(Number = sum(nchip, na.rm = TRUE), .groups = "drop") |>
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(month) |>
  e_bars_stacked("month") |>
  e_y_axis(name = "# of L2 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-l2-week, echo = FALSE, warning = FALSE}
data %>% 
  mutate(week = as.factor(week)) |>
  group_by(sensor, week) %>%
  summarise(Number = sum(nchip, na.rm = TRUE), .groups = "drop") |>
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(week) |>
  e_bars_stacked("week") |>
  e_y_axis(name = "# of L2 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

## Coverages

Data cover is the percentage of valid pixels in an input image, i.e. excl. the black border or SLC-off stripes.
Cloud cover includes opaque clouds + buffer, cloud shadows + buffer and cirrus clouds.
Snow and cloud are not mutually exclusive, i.e. a cloud can be classified as snow, too.
Clear scene includes any valid pixels not tagged as cloud, cloud shadow or snow.
Clear land further excludes water pixels.
*Processing status is not taken into account.*
  
```{r plot-cover, echo = FALSE, warning = FALSE}
data %>% 
  pivot_longer(cols = c("dc", "cc", "sc", "wc", "ac", "lc"), names_to = "cover", values_to = "Number") |>
  mutate(cover = gsub("dc", "data", cover)) |>
  mutate(cover = gsub("cc", "cloud", cover)) |>
  mutate(cover = gsub("sc", "snow", cover)) |>
  mutate(cover = gsub("wc", "water", cover)) |>
  mutate(cover = gsub("ac", "all land", cover)) |>
  mutate(cover = gsub("lc", "clear land", cover)) |>
  group_by(cover) |>
  e_charts() |>
  e_boxplot(Number) |>
  e_y_axis(name = "% cover", nameLocation = "middle") |>
  e_tooltip(trigger = "item")
```

The following plots show the mean cover per year, month and week.

```{r plot-cover-by-year, echo = FALSE, warning = FALSE}
data %>% 
  mutate(year = as.factor(year)) |>
  group_by(year) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) |>
  arrange(year) |>
  e_charts(year) |>
  e_line(dc, name = "data") |>
  e_line(cc, name = "cloud") |>
  e_line(sc, name = "snow") |>
  e_line(wc, name = "water") |>
  e_line(ac, name = "clear all") |>
  e_line(lc, name = "clear land") |>
  e_y_axis(name = "% cover", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("coverage")
```

```{r plot-cover-by-month, echo = FALSE, warning = FALSE}
data %>% 
  mutate(month = as.factor(month)) |>
  group_by(month) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) |>
  arrange(month) |>
  e_charts(month) |>
  e_line(dc, name = "data") |>
  e_line(cc, name = "cloud") |>
  e_line(sc, name = "snow") |>
  e_line(wc, name = "water") |>
  e_line(ac, name = "clear all") |>
  e_line(lc, name = "clear land") |>
  e_y_axis(name = "% cover", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("coverage")
```

```{r plot-cover-by-week, echo = FALSE, warning = FALSE}
data %>% 
  mutate(week = as.factor(week)) |>
  group_by(week) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) |>
  arrange(week) |>
  e_charts(week) |>
  e_line(dc, name = "data") |>
  e_line(cc, name = "cloud") |>
  e_line(sc, name = "snow") |>
  e_line(wc, name = "water") |>
  e_line(ac, name = "clear all") |>
  e_line(lc, name = "clear land") |>
  e_y_axis(name = "% cover", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("coverage")
```

## Aerosol Optical depth

```{r plot-aod-status, echo = FALSE, warning = FALSE}
data |>
  filter(status == "Success") |>
  count(aod_status, name = "Number") |>
  e_charts(aod_status) |>
  e_pie(Number, radius = c("30%", "70%"), roseType = "radius") |>
  e_tooltip(trigger = "item")
```

```{r plot-aod-targets, echo = FALSE, warning = FALSE}
data |>
  filter(status == "Success") |>
  pivot_longer(cols = c("nwater", "nveg"), names_to = "target", values_to = "Number") |>
  mutate(target = gsub("nwater", "dark water", target)) |>
  mutate(target = gsub("nveg", "dark dense vegetation", target)) |>
  group_by(target) |>
  e_charts() |>
  e_boxplot(Number) |>
  e_y_axis(name = "# of targets", nameLocation = "middle") |>
  e_tooltip(trigger = "item")
```

```{r plot-aod, echo = FALSE, warning = FALSE}
data |>
  filter(status == "Success") |>
  e_charts() |>
  e_density(aod) |>
  e_y_axis(name = "AOD", nameLocation = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_legend(show = FALSE)
```

```{r plot-aod-by-year, echo = FALSE, warning = FALSE}
data %>% 
  filter(status == "Success") |>
  mutate(year = as.factor(year)) |>
  group_by(year) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) |>
  arrange(year) |>
  e_charts(year) |>
  e_line(aod, name = "AOD") |>
  e_y_axis(name = "AOD", nameLocation = "middle") |>
  e_legend(show = FALSE) |>
  e_tooltip(trigger = "axis") |>
  e_datazoom()
```

```{r plot-aod-by-month, echo = FALSE, warning = FALSE}
data %>% 
  filter(status == "Success") |>
  mutate(month = as.factor(month)) |>
  group_by(month) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) |>
  arrange(month) |>
  e_charts(month) |>
  e_line(aod, name = "AOD") |>
  e_y_axis(name = "AOD", nameLocation = "middle") |>
  e_legend(show = FALSE) |>
  e_tooltip(trigger = "axis") |>
  e_datazoom()
```

```{r plot-aod-by-week, echo = FALSE, warning = FALSE}
data %>% 
  filter(status == "Success") |>
  mutate(week = as.factor(week)) |>
  group_by(week) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) |>
  arrange(week) |>
  e_charts(week) |>
  e_line(aod, name = "AOD") |>
  e_y_axis(name = "AOD", nameLocation = "middle") |>
  e_legend(show = FALSE) |>
  e_tooltip(trigger = "axis") |>
  e_datazoom()
```

## Coregistration

Coregistration failed for
`r data %>% filter(status == "Coregistration failed") %>% nrow()`
Level 1 images.

```{r plot-month-coreg, echo = FALSE, warning = FALSE}

data %>% 
  filter(status == "Coregistration failed") |>
  mutate(month = as.factor(month)) |>
  count(sensor, month, name = "Number") |>
  arrange(sensor) |>
  pivot_wider(names_from = sensor, values_from = Number) |>
  arrange(month) |>
  e_bars_stacked("month") |>
  e_y_axis(name = "# of L1 images", nameLocation = "middle") |>
  e_legend(right = 0, orient = "vertical", top = "middle") |>
  e_tooltip(trigger = "axis") |>
  e_datazoom() |>
  e_group("sensor")
```

```{r plot-cover-coreg, echo = FALSE, warning = FALSE}
data %>% 
  filter(status == "Coregistration failed") |>
  pivot_longer(cols = c("dc", "cc", "sc", "wc", "ac", "lc"), names_to = "cover", values_to = "Number") |>
  mutate(cover = gsub("dc", "data", cover)) |>
  mutate(cover = gsub("cc", "cloud", cover)) |>
  mutate(cover = gsub("sc", "snow", cover)) |>
  mutate(cover = gsub("wc", "water", cover)) |>
  mutate(cover = gsub("ac", "all land", cover)) |>
  mutate(cover = gsub("lc", "clear land", cover)) |>
  group_by(cover) |>
  e_charts() |>
  e_boxplot(Number) |>
  e_y_axis(name = "# cover", nameLocation = "middle") |>
  e_tooltip(trigger = "item")
```

## Runtime

The following plot summarizes the runtime for each image by sensor and processing status.
The runtime is the required real-time of each process (time between process start and end).
This measure may deviate from CPU-time due to multithreading etc.

```{r plot-runtime, echo = FALSE, warning = FALSE}
p1 <- data %>% 
  filter(status == "Success") |>
  group_by(sensor) |>
  e_charts(elementId = "runtime1") |>
  e_boxplot(time) |>
  e_y_axis(name = "runtime [minutes]", nameLocation = "middle") |>
  e_tooltip(trigger = "item")

p2 <- data %>% 
  filter(status == "Too cloudy") |>
  group_by(sensor) |>
  e_charts(elementId = "runtime2") |>
  e_boxplot(time) |>
  e_y_axis(name = "runtime [minutes]", nameLocation = "middle") |>
  e_tooltip(trigger = "item") |> 
  e_connect(c("runtime1", "runtime2")) # connect

e_arrange(p1, p2)
```

```{r write-csv, echo = FALSE, warning = FALSE}
write.csv(data, file = params$ftable, row.names = FALSE)
```
