---
title: "FORCE Level 2 Processing Report"
date: "`r Sys.Date()`"
output: html_document
params:
  dlog: "log"
---

```{r load-packages, include = FALSE}
require(dplyr)
require(plotly)
```

```{r load-data, include = FALSE}
flog = params$dlog %>% dir(".log$", full.names=TRUE)
nlog = flog %>% length()

log = "character" %>% vector(nlog)

for (i in 1:nlog){ 
  log[i] = flog[i] %>%
           readLines() %>%
           paste(collapse = " ")
}
```


```{r prepare-data, include = FALSE}
status = rep("Error", nlog)
status[grep("Success", log)]      <- "Success"
status[grep("Skip", log)]         <- "Too cloudy"
status[grep("coreg failed", log)] <- "Coregistration failed"
status = status %>% as.factor()
nfail = sum(status == "Error")

mm = log %>% 
     { gsub(".*([0-9]{2}) mins.*", "\\1", .) } %>% 
     as.numeric()
ss = log %>% 
     { gsub(".*([0-9]{2}) secs.*", "\\1", .) } %>% 
     as.numeric()
time = mm + ss/60

id = log %>%
     { gsub(":.*", "", .) } %>% 
     basename()

id_split = id %>% strsplit("_")

sensor = id_split %>% sapply("[", 1)

date = id_split %>% 
       sapply(function(x){
         grep("^[0-9]{8}", x, value = TRUE) %>%
         first() }) %>%
       substr(1, 8) %>%
       strptime("%Y%m%d")

dc = log %>%
     { gsub(".*dc: ([^%]*)%.*", "\\1", .) } %>%
     as.numeric()

cc = log %>%
     { gsub(".*cc: ([^%]*)%.*", "\\1", .) } %>%
     as.numeric()

sc = log %>%
     { gsub(".*sc: ([^%]*)%.*", "\\1", .) } %>%
     as.numeric()

wc = log %>%
     { gsub(".*wc: ([^%]*)%.*", "\\1", .) } %>%
     as.numeric()

ac = 100 %>% 
     -(cc+sc) %>%
     pmax(0)
lc = 100 %>%
     -(cc+sc+wc) %>%
     pmax(0)

aod = log %>%
      { gsub(".*AOD: (.*)\\. #.*", "\\1", .) } %>%
      as.numeric()

nwater = log %>%
         { gsub(".*# of targets: ([0-9]*)/.*", "\\1", .) } %>%
         as.integer()

nveg   = log %>%
         { gsub(".*# of targets: [0-9]*/([0-9]*).*", "\\1", .) } %>%
         as.integer()

aod_status = rep("NA", nlog)
aod_status[(nwater + nveg) == 0] = "AOD estimation failed"
aod_status[(nwater + nveg)  > 0] = "AOD estimation successful"
aod_status = aod_status %>% as.factor()

nchip = log %>%
        { gsub(".* ([0-9]*) product.*", "\\1", .) } %>%
        as.integer()

data = data.frame(status,
                  sensor, 
                  nchip, 
                  time,
                  date,
                  year  = format(date, "%Y"),
                  month = format(date, "%m"),
                  week  = format(date, "%W"),
                  doy   = format(date, "%j"),
                  dc,
                  cc,
                  sc,
                  wc,
                  ac,
                  lc,
                  aod_status,
                  aod,
                  nwater,
                  nveg,
                  log,
                  id)
```


# Processing status

`r nlog` Level 1 images were processed. 
`r nfail` images failed.

```{r plot-status, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     count(status), 
              labels = ~status, values = ~n, type = 'pie')
fig
```


```{r failed-images, echo = FALSE}
if (nfail > 0){
  data %>% filter(status == "Error") %>% select(log)
}
```


# Number of Level 1 images

The following plots count the number of processed Level 1 images per sensor, year, month and week.
*Processing status is not taken into account.*


```{r plot-l1-sensor, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>% 
                     count(sensor), 
              x = ~sensor, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L1 images'))
fig
```

```{r plot-l1-year, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>% 
                     count(sensor, year), 
              x = ~year, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L1 images'), barmode = 'stack')
fig
```

```{r plot-l1-month, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>% 
                     count(sensor, month), 
              x = ~month, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L1 images'), barmode = 'stack')
fig
```

```{r plot-l1-week, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>% 
                     count(sensor, week), 
              x = ~week, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L1 images'), barmode = 'stack')
fig
```


# Number of Level 2 images

The following plots count the number of processed Level 2 image chips per sensor, year, month and week.

```{r plot-l2-sensor, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>% 
                     group_by(sensor) %>% 
                     summarise(n = sum(nchip, na.rm = TRUE), .groups = "drop"),
              x = ~sensor, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L2 images'))
fig
```

```{r plot-l2-year, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%  
                     group_by(sensor, year) %>% 
                     summarise(n = sum(nchip, na.rm = TRUE), .groups = "drop"),
              x = ~year, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L2 images'), barmode = 'stack')
fig
```

```{r plot-l2-month, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%  
                     group_by(sensor, month) %>% 
                     summarise(n = sum(nchip, na.rm = TRUE), .groups = "drop"),
              x = ~month, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L2 images'), barmode = 'stack')
fig
```

```{r plot-l2-week, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%  
                     group_by(sensor, week) %>% 
                     summarise(n = sum(nchip, na.rm = TRUE), .groups = "drop"),
              x = ~week, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L2 images'), barmode = 'stack')
fig
```



# Coverages

Data cover is the percentage of valid pixels in an input image, i.e. excl. the black border or SLC-off stripes.
Cloud cover includes opaque clouds + buffer, cloud shadows + buffer and cirrus clouds. 
Snow and cloud are not mutually exclusive, i.e. a cloud can be classified as snow, too.
Clear scene includes any valid pixels not tagged as cloud, cloud shadow or snow.
Clear land further excludes water pixels.
*Processing status is not taken into account.*

```{r plot-cover, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data, 
                y = ~dc, name = "data", type = 'box') %>%
      add_trace(y = ~cc, name = "cloud") %>%
      add_trace(y = ~sc, name = "snow") %>%
      add_trace(y = ~wc, name = "water") %>%
      add_trace(y = ~ac, name = "clear scene") %>%
      add_trace(y = ~lc, name = "clear land") %>%
      layout(yaxis = list(title = '% cover'))
fig
```

The following plots show the mean cover per year, month and week.


```{r plot-cover-by-year, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     group_by(year) %>%
                     summarise_all(mean, na.rm = TRUE),
              x = ~year, y = ~dc, name = "data", type = 'scatter', mode = 'lines+markers') %>%
    add_trace(x = ~year, y = ~cc, name = "cloud") %>%
    add_trace(x = ~year, y = ~sc, name = "snow") %>%
    add_trace(x = ~year, y = ~wc, name = "water") %>%
    add_trace(x = ~year, y = ~ac, name = "clear all") %>%
    add_trace(x = ~year, y = ~lc, name = "clear land") %>%
    layout(yaxis = list(title = '% cover'))
fig
```

```{r plot-cover-by-month, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     group_by(month) %>%
                     summarise_all(mean, na.rm = TRUE),
              x = ~month, y = ~dc, name = "data", type = 'scatter', mode = 'lines+markers') %>%
    add_trace(x = ~month, y = ~cc, name = "cloud") %>%
    add_trace(x = ~month, y = ~sc, name = "snow") %>%
    add_trace(x = ~month, y = ~wc, name = "water") %>%
    add_trace(x = ~month, y = ~ac, name = "clear all") %>%
    add_trace(x = ~month, y = ~lc, name = "clear land") %>%
    layout(yaxis = list(title = '% cover'))
fig
```

```{r plot-cover-by-week, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     group_by(week) %>%
                     summarise_all(mean, na.rm = TRUE),
              x = ~week, y = ~dc, name = "data", type = 'scatter', mode = 'lines+markers') %>%
    add_trace(x = ~week, y = ~cc, name = "cloud") %>%
    add_trace(x = ~week, y = ~sc, name = "snow") %>%
    add_trace(x = ~week, y = ~wc, name = "water") %>%
    add_trace(x = ~week, y = ~ac, name = "clear all") %>%
    add_trace(x = ~week, y = ~lc, name = "clear land") %>%
    layout(yaxis = list(title = '% cover'))
fig
```


# Aerosol Optical depth

```{r plot-aod-status, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     filter(status == "Success") %>%
                     count(aod_status), 
              labels = ~aod_status, values = ~n, type = 'pie')
fig
```

```{r plot-aod-targets, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     filter(status == "Success"), 
                y = ~nwater, name = "dark water", type = 'box') %>%
      add_trace(y = ~nveg, name = "dark dense vegetation")
fig
```

```{r plot-aod, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     filter(status == "Success"), 
                y = ~aod, name = "AOD", type = 'box')
fig
```

```{r plot-aod-by-year, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     filter(status == "Success") %>%
                     group_by(year) %>%
                     summarise_all(mean, na.rm = TRUE),
              x = ~year, y = ~aod, name = "AOD", type = 'scatter', mode = 'lines+markers') %>%
      layout(yaxis = list(title = 'AOD'))
fig
```


```{r plot-aod-by-month, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     filter(status == "Success") %>%
                     group_by(month) %>%
                     summarise_all(mean, na.rm = TRUE),
              x = ~month, y = ~aod, name = "AOD", type = 'scatter', mode = 'lines+markers') %>%
      layout(yaxis = list(title = 'AOD'))
fig
```


```{r plot-aod-by-week, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     filter(status == "Success") %>%
                     group_by(week) %>%
                     summarise_all(mean, na.rm = TRUE),
              x = ~week, y = ~aod, name = "AOD", type = 'scatter', mode = 'lines+markers') %>%
      layout(yaxis = list(title = 'AOD'))
fig
```


# Coregistration

Coregistration failed for 
`r data %>% filter(status == "Coregistration failed") %>% nrow()` 
Level 1 images.

```{r plot-month-coreg, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     filter(status == "Coregistration failed") %>%
                     count(sensor, month), 
              x = ~month, y = ~n, color = ~sensor, type = 'bar') %>%
      layout(yaxis = list(title = '# of L1 images'), barmode = 'stack')
fig
```

```{r plot-cover-coreg, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data %>%
                     filter(status == "Coregistration failed"), 
                y = ~dc, name = "data", type = 'box') %>%
      add_trace(y = ~cc, name = "cloud") %>%
      add_trace(y = ~sc, name = "snow") %>%
      add_trace(y = ~wc, name = "water") %>%
      add_trace(y = ~ac, name = "clear all") %>%
      add_trace(y = ~lc, name = "clear land") %>%
      layout(yaxis = list(title = '% cover'))
fig
```


# Runtime

The following plot summarizes the runtime for each image by sensor and processing status. 
The runtime is the required real-time of each process (time between process start and end).
This measure may deviate from CPU-time due to multithreading etc. 

```{r plot-runtime, echo = FALSE, warning = FALSE}
fig = plot_ly(data = data, 
              x = status, y = ~time, color = ~sensor, type = 'box') %>%
      layout(yaxis = list(title = 'runtime [minutes]'), boxmode = "group")
fig
```

